\chapter*{Abstract} % no number
\label{abtract}

\addcontentsline{toc}{chapter}{Abstract} % add to index
\vspace{0.4 cm}

In the dynamic landscape of software testing, automated test generation plays a pivotal role in ensuring the reliability and robustness of software applications. However, a prevalent challenge in traditional automated testing tools lies in their reliance on code implementation for test generation, leading to the Oracle problem. This issue arises when deviations in the code are mistakenly considered as the expected behavior of the program. To address this concern, our research introduces EvoOracle, an approach that leverages Large Language Models (LLMs). Unlike traditional methods, LLMs are trained on extensive data corpora, allowing them to discern the intended behavior of a system under test irrespective of code intricacies. EvoOracle comprises three key components: a preprocessor, an oracle generator, and a validation module. Our approach involves a sophisticated interaction between automated test generation tools and LLMs, leveraging dynamic prompts and iterative processes. Through comprehensive experimentation across diverse LLM models, we scrutinize the quality, performance, and practical integration aspects of EvoOracle-generated assertions. In our exploration of EvoOracle's capabilities, we tackled three pivotal questions. Firstly, we delved into the quality of EvoOracle-generated oracles through experiments involving five diverse LLMs, 146 unique test methods for 9 diverse classes from 4 differen projects, and 9932 attempts. Results revealed syntax errors in 17.85\%, compile errors in 22.05\%, runtime errors in 2.18\%, and successful assertion generation in 9.26\% of instances. Secondly, we scrutinized EvoOracle's performance in assertion generation against Evosuite. Finally, we analyzed EvoOracle's potential in enhancing EvoSuite's performance by comparing baseline metrics with EvoSuite complemented by assertions from five LLMs. The nuanced variations in performance metrics shed light on EvoOracle's impact on test suite quality, marking a significant stride in understanding its practical implications in software testing contexts.